\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage{multicol}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\usepackage{amsmath}

\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.4in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
    \vspace{-4pt}\scshape\raggedright\large\bfseries\color{ForestGreen}
}{}{0em}{}[\color{ForestGreen}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
    \item\small{
        {#1 \vspace{-2pt}}
    }
}

\newcommand{\classesList}[4]{
    \item\small{
        {#1 #2 #3 #4 \vspace{-2pt}}
    }
}

\newcommand{\resumeSubheading}[4]{
    \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
        \textbf{#1} & \textbf{\small #2} \\
        \text{\small#3} & \text{\small #4} \\
    \end{tabular*}\vspace{-10pt}
}

\newcommand{\resumeSubheadingDouble}[6]{
    \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{@{}l@{\extracolsep{\fill}}r@{}}
        \textbf{\Large #1} & \textbf{\Large \small #2} \\
        \text{\small#3} & \text{\small #4} \\
        \textbf{#5} & \textbf{\small #6} \\
    \end{tabular*}\vspace{-7pt}
}


\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
        \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{1.001\textwidth}{l@{\extracolsep{\fill}}r}
        \small#1 & \textbf{\small #2}\\
    \end{tabular*}\vspace{-18pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemi{$\vcenter{\hbox{\tiny$\bullet$}}$}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.0in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{
    \begin{itemize}[label=\textcolor{ForestGreen}{\textbullet}]
}
\newcommand{\resumeItemListEnd}{
    \end{itemize}
    \vspace{-5pt}
}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}
\begin{center}
    {\Huge \scshape \textcolor{ForestGreen}{Prabhath Chellingi}} \\ 
    \textcolor{ForestGreen}{{\small \textit{ML Research Engineer | LLM Systems | Agentic AI | Knowledge Graphs}}} \\
    \vspace{-9pt}
    \bigskip

    \textcolor{ForestGreen}{
        \small Phone: +91-9963771971 | Email: \href{mailto:prabhathchellingi2003@gmail.com}{prabhathchellingi2003@gmail.com} | 
        LinkedIn: \href{https://linkedin.com/in/prabhath-chellingi/}{linkedin.com/in/prabhath-chellingi} | 
        GitHub: \href{https://github.com/Prabhath003}{github.com/Prabhath003}
    }
    \vspace{-8pt}
\end{center}

\section{About}
ML Research Engineer with expertise in \textbf{LLM reasoning}, \textbf{Agentic AI systems}, \textbf{Knowledge Graphs}, and \textbf{RAG architectures}. Specialized in fine-tuning Small Language Models and designing \textbf{graph-augmented retrieval systems} to reduce hallucinations and improve factual grounding. Proven track record building \textbf{scalable inference pipelines}, \textbf{autonomous agents}, \textbf{semantic search engines}, and \textbf{knowledge-aware retrieval systems}. Passionate about advancing trustworthy, interpretable, and efficient AI systems.
\vspace{-8pt}

% -----------EDUCATION-----------
\section{Education}
    \resumeSubHeadingListStart
        \resumeSubheading
            {Indian Institute of Technology, Hyderabad}{}
            {\textit{B.Tech. in Computer Science and Engineering | Grade 8.52}}{2020 - 2024}
            \vspace{-15pt}
        \resumeSubheading{}{}
            {\textit{Minor in Entrepreneurship | Grade 8.92}}{2022 - 2024}
    \resumeSubHeadingListEnd

\section{Research Publications}
    \begin{itemize}[leftmargin=0.5in,label={}]
        \item Prajwal Ganugula, Y. S. S. S. Santosh Kumar, N. K. Sagar Reddy, \textbf{Prabhath Chellingi}, Avinash Thakur, Neeraj Kasera, and C. Shyam Anand \\
        \textbf{\href{https://openaccess.thecvf.com/content/ICCV2023W/NIVT/html/Ganugula_MOSAIC_Multi-Object_Segmented_Arbitrary_Stylization_Using_CLIP_ICCVW_2023_paper.html}{Multi-Object Segmented Arbitrary Stylization Using CLIP}} \\
        \textit{ICCV Workshop, 2023}
    \end{itemize}
    \vspace{-18pt}

%-----------EXPERIENCE-----------
\section{Work Experience}
    \resumeSubHeadingListStart
        \resumeSubheading   
            {Stealth Startup - GiKA.ai}{}
            {\textit{Founding ML Engineer}}{Jun 2024 - Present}
            \resumeItemListStart
                \resumeItem{\textbf{Agentic AI Systems \& Reasoning Platform}: 
                Developed an \textbf{in-house agentic framework (LangGraph-like)} supporting multi-step LLM reasoning, planning, tool invocation, and memory management for autonomous execution of complex workflows.}
                
                \resumeItem{Designed and deployed \textbf{agentic planners and pipelines} with terminal and web access for autonomous data gathering, real-time analytics, and \textbf{knowledge graph construction and traversal} from heterogeneous sources.}
            
                \resumeItem{\textbf{Model Optimization \& Knowledge-Aware Learning}: 
                Fine-tuned \textbf{Small Language Models} (LLaMA-3.1-8B, Gemma-2-9B) for \textbf{knowledge graph-aware reasoning}, improving structured inference and factual grounding in downstream tasks.}
            
                \resumeItem{\textbf{Commercial AI Applications \& Impact}:}
                    \begin{itemize}[leftmargin=0.25in]
                        \item \small Developed an \textbf{Agentic JSON Builder} for large-scale structured data completion  
                        \item \small Autonomously populated \textbf{8,000+ fields} via context-aware retrieval, reducing manual effort by \textbf{95\%}
                        \item \small Built a \textbf{low-latency Voice AI Agent} for edtech sales platform achieving \textbf{sub-300ms latency}
                        \item \small Delivered \textbf{90\%+ intent accuracy} covering \textbf{1,500+ courses} with real-time inference
                    \end{itemize}
            
                \resumeItem{\textbf{Knowledge-Driven Search \& Web Intelligence}: 
                Engineered a \textbf{knowledge graph-powered semantic search engine} enabling intent-based product discovery with improved retrieval accuracy and user engagement.}
            
                \resumeItem{Developed scalable \textbf{web intelligence infrastructure}, including universal HTML-to-structured-data parser and Playwright/Selenium-based crawler supporting dynamic interactions (20s/page).}
                \resumeItem{Researched and implemented advanced \textbf{coreference resolution} and \textbf{entity linking} pipelines (GPT-4, LLaMA3, SpanBERT, LingMess) validating superiority of \textbf{Knowledge Graphs over vector databases} in RAG systems.}
            \resumeItemListEnd
            \vspace{-10pt}
        \resumeSubheading
            {OnePlus/Oppo(OPLUS) Mobiles India R\&D}{}
            {\textit{Innovation Research Intern}}{Jan 2023 - Jun 2023}
            \resumeItemListStart
                \resumeItem{Contributed to \textbf{MOSAIC} (Multi-Object Segmented Arbitrary Image Stylization), accepted at \textbf{ICCV'23 workshop}; performed extensive ablation studies on key models (ITNet, StyTr2, HDRNet).}
                \resumeItem{Compressed Dumoulin-style CNN networks for edge deployment, achieving \textbf{8x size reduction} and \textbf{11x FLOPs optimization} using quantization and pruning techniques.}
                \resumeItem{Developed \textbf{ODASH}, a debugging tool for R\&D teams, implementing full-stack web app with KNN search on log embeddings for anomaly detection.}
            \resumeItemListEnd
            \vspace{-2pt}
        \resumeSubheading
            {Personifwy}{}
            {\textit{AI Intern Trainee}}{Jan 2022 - Mar 2022}
            \resumeItemListStart
                \resumeItem{Executed end-to-end ML projects in image processing and NLP including news classification, handwritten digit recognition, and fashion object detection using CNNs, OpenCV, scikit-learn, and TensorFlow.}
            \resumeItemListEnd
            \vspace{-2pt}
        \resumeSubheading
            {Indian Institute of Technology, Hyderabad}{}
            {\textit{Research Assistant under Prof. Saketha Nath}}{2024}
            \resumeItemListStart
                \resumeItem{\textbf{RamayanaGPT - Knowledge Retrieval System}: Designed a context-aware retrieval system for knowledge-based QA. Built a graph-based retrieval engine linking database chunks via semantic entities and edges to reduce LLM hallucinations.}
            \resumeItemListEnd
    \resumeSubHeadingListEnd
    \vspace{-18pt}

%-----------PROJECTS-----------
\section{Projects}
    \vspace{-5pt}
    \resumeSubHeadingListStart
        \resumeProjectHeading
            {\href{https://github.com/Prabhath003/AgenticRAG.git}{\textbf{AgenticRAG}}
            - \textit{Autonomous Retrieval-Augmented Generation System}}{2025}
            \resumeItemListStart
                \resumeItem{Developed agentic RAG framework enabling chunk-level traversal and document jumping, mimicking human-like reasoning and exploration across large knowledge corpora (10K+ documents).}
                \resumeItem{Engineered with adaptive context management and multi-hop reasoning, improving factual accuracy by 25\% and contextual depth in generation.}
            \resumeItemListEnd
            \vspace{-15pt}
        \resumeProjectHeading
            {\href{https://github.com/Prabhath003/model-inference-server.git}{\textbf{LLM Inference Server}} - \textit{Distributed GPU Management}}{2025}
            \resumeItemListStart
                \resumeItem{Open-sourced GPU-optimized inference server for HuggingFace models with dynamic model offloading and loading capabilities.}
                \resumeItem{Designed as central access node within MCP protocols, serving 10+ concurrent GPU tasks across distributed servers, providing OLLAMA alternative with enhanced performance.}
            \resumeItemListEnd
            \vspace{-15pt}
        \resumeProjectHeading 
            {\textbf{Finance Time Series Forecasting with MixerMLP} - \textit{PyTorch, Neural Networks}}{2023}
            \resumeItemListStart
                \resumeItem{Adapted MixerMLP architecture for financial time series prediction with novel input format for tabular data representation.}
                \resumeItem{Achieved low MSE of 1.3 x 10-3 on benchmark datasets, demonstrating superior performance for temporal pattern recognition.}
            \resumeItemListEnd
    \resumeSubHeadingListEnd

\section{Licenses \& Certifications}
    \resumeSubHeadingListStart
        \resumeProjectHeading
            {\textbf{Ethical Hacking and Cyber Security Masterclass} - \textit{Udemy}}{Jan 2025}
            \resumeItemListStart
                \resumeItem{Comprehensive training in ethical hacking, penetration testing, network security, vulnerability assessment, and cybersecurity defense mechanisms.}
            \resumeItemListEnd
            \vspace{-15pt}
        \resumeProjectHeading
            {\textbf{MongoDB Developer Toolkit} - \textit{GeeksforGeeks}}{Dec 2024}
            \resumeItemListStart
                \resumeItem{Advanced MongoDB skills: replication, sharding, indexing, aggregation framework, data modeling, NoSQL database design and optimization with Atlas.}
            \resumeItemListEnd
            \vspace{-15pt}
        \resumeProjectHeading
            {\textbf{IBM Statistics 101 Badge} - \textit{IBM Developer Skills Network}}{2022}
            \vspace{-15pt}
        \resumeProjectHeading
            {\textbf{Top 5 Finalist - Novus X.0 Electronic Prototype Competition}}{2021}
            \vspace{-15pt}
        \resumeProjectHeading
            {\textbf{JEE Advanced All India Rank 1689 | JEE Mains All India Rank 2345}}{2020}
    \resumeSubHeadingListEnd
\vspace{2pt}

%-----------PROGRAMMING SKILLS-----------
\section{Technical Skills}
    \begin{itemize}[leftmargin=0.15in, label={}]
        \item{
            \textbf{Languages:} Python, C++, Java, JavaScript, SQL, HTML, CSS \\
            \textbf{Frameworks \& Libraries:} PyTorch, TensorFlow, Flask, Celery, OpenCV, ROS, FastAPI, LangChain, Hugging Face \\
            \textbf{Tools \& Platforms:} Git, Docker, pgAdmin4, Android Studio, OpenSearch, Neo4j, Playwright, MongoDB, Linux Shell Scripting \\
            \textbf{Specialized Skills:} LLM Fine-tuning, Retrieval-Augmented Generation (RAG), Knowledge Graphs, Agentic AI, vLLM, BitsAndBytes, Prompt Engineering \\
            \textbf{ML Specializations:} Model Optimization, Inference Pipeline Design, Entity Linking, Coreference Resolution, Semantic Search, Vector Databases
        }
    \end{itemize}
    \vspace{-20pt}

%-----------INVOLVEMENT---------------
\section{Leadership \& Extracurricular}
    \resumeItemListStart
        \resumeItem{\textbf{Core Member - Robotix (IITH Robotics Club)}}
        \vspace{-2pt}
        \resumeItem{\textbf{Publicity Volunteer - Elan \& Envision (IITH Tech Fest)}}
    \resumeItemListEnd

\end{document}